Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2019-07-08 manuscript/phylogenetic_signal_manuscript.tex
trimmed summary to fit word limit, small formatting tweaks

\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth Hasle$^{4}$,\\
Joshua A. Thia$^{1,5}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
\medskip$^2$Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
\medskip$^5$Present Address: School of Biological Sciences\\
University of Queensland\\Brisbane, QLD 4072, Australia }

@@

\section*{Summary}

  \begin{itemize}
    \item Related plants are often hypothesised to interact with similar sets of 
          pollinators and herbivores, but empirical support for this idea is mixed.
          Here we argue that this may be because some plant families vary in their 
          tendency to share interaction partners.

    \item We introduce a novel approach with which to quantify
          overlap of interaction
          partners for each pair of plants in 59 pollination and 11 herbivory
          networks based on the numbers of potential interaction partners which are shared and not shared.  We then tested for relationships between phylogenetic 
          distance and partner overlap within each network, and whether these 
          relationships varied with the composition of the plant community.
          Finally, we tested for different relationships within well-represented
          plant families.

    \item Across all networks, more closely-related plants tended to have 
          greater overlap, and this tendency was stronger in herbivory 
          networks than pollination networks. While the strength of this relationship within a network was not related to the composition of the network's plant component, we nevertheless found that different plant families showed different relationships between phylogenetic distance and overlap of interaction partners.

    \item The variety of relationships between phylogenetic distance and
          interaction partners in different plant families likely
          reflects a comparable variety of ecological and evolutionary processes. To 
          understand the distribution of interactions within a community, 
          it is therefore important to consider factors affecting particular 
          plant families.

>>>>

\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth Hasle$^{4}$,\\
Joshua A. Thia$^{1,5}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^2$Present address: Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
\medskip$^5$Present Address: School of Biological Sciences\\
University of Queensland\\Brisbane, QLD 4072, Australia }

@@

\section*{Summary} % Must be <200 words. Currently 199

  \begin{itemize}
    \item Related plants are often hypothesised to interact with similar sets of pollinators and herbivores, but empirical support for this idea is mixed. We argue that this may be because plant families vary in their tendency to share interaction partners.

    \item We introduce a novel way to quantify overlap of interaction partners for each pair of plants in 59 pollination and 11 herbivory networks based on the numbers of shared and unshared interaction partners.  We test for relationships between phylogenetic distance and partner overlap within each network, and whether these relationships varied with the composition of the plant community. Finally, we test for different relationships within well-represented plant families.

    \item Across all networks, more closely-related plants tended to have greater overlap, especially in herbivory networks. The strength of this relationship within a network was unrelated to the composition of the network's plant component, but different plant families showed different relationships between phylogenetic distance and overlap of interaction partners.

    \item The variety of relationships between phylogenetic distance and partner overlap in different plant families likely reflects a comparable variety of ecological and evolutionary processes. Considering factors affecting the dominant plant families within a community may be the key to understanding the distribution of interactions.
